Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*

### 2019-01-11 analyses/reproduce_analyses.Rmd
testing as github_document

---
title: "Reproduce Analyses Reported in "Phenotypic evolution is more constrained in simpler food webs""
author: "Matthew A. Barbour"
date: "`r Sys.Date()`"
output: github_document
# Trying github_document for easy viewing on github
#  prettydoc::html_pretty:
#    theme: architect
#    highlight: github
fontsize: 12pt
---

@@

  # subset data for analysis
  filter(phenology == "early", Location == "tree",
         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
  filter(Treatment.focus == "Ectoparasitoid exclusion" & ectos < 1 | Treatment.focus == "Control") %>% # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
  mutate(Foodweb = ifelse(Treatment.focus=="Control","Complex","Simple"),
         gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
         sc.Diam = as.numeric(scale(Gall_Height_mm)), 
         sc.log.Clutch = as.numeric(scale(log(gall_individuals))), 
         sc.sqrt.Pref = as.numeric(scale(sqrt(Density_per_100_shoots))))

@@

## Bootstrap fitness estimates
bootstrap_fitness <- function(logistic_model, #fixed_effects, 
                              newdata, bootstraps, intervals=c(0.025,0.975)){
  #model_matrix <- model.matrix(formula(fixed_effects), newdata)

  # Absolute fitness
  get_absolute_fitness <- function(.) predict(., newdata=newdata, type="response", re.form=~0) #inverse_logit(model_matrix %*% fixef(.))

@@

  if(is.null(bootstraps) == FALSE){
    get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

@@

## Predicting evolutionary dynamics 
evolutionary_dynamics <- function (betas,    # one-column matrix of directional selection gradients
                                   gammas,   # matrix of nonlinear selection gradients
                                   G_0,      # initial G-matrix
                                   z_0,      # one-column matrix of initial trait values
                                   t) {       # evolutionary time steps 
    # Equation 2 from Phillips and Arnold 1989, Evolution
    G <- rep(list(G_0), t) 
    for (i in 1:t) G[[i + 1]] <- {
      G[[i]] + G[[i]] %*% (gammas - betas %*% t(betas)) %*% G[[i]] # may need to add mutation/recombination matrix (see Phillips and Arnold 1989)
    }

    # Equation 1 from Phillips and Arnold 1989, Evolution
    z <- rep(list(z_0), t) 
    for (i in 1:t) z[[i + 1]] <- {
        z[[i]] + G[[i]] %*% betas
    }
    return(list(z=z,G=G))
}

## Number of evolutionary time steps for simulation
n_evo_sims <- 200 # 1000

## Tidy up evolutionary simulations
tidy_evo_sims <- function(evo_sims) {
  tidy_sim <- data.frame(matrix(unlist(evo_sims$z), ncol=3, byrow=T)) %>% 
    transmute(Time=1:length(evo_sims$z), Diam=round(X1,2), Clutch=round(X2,2), Pref=round(X3,2)) %>%
    filter(Diam < 1, Diam > -1, Clutch < 1, Clutch > -1, Pref < 1, Pref > -1)

  return(tidy_sim)
}

@@

## Color palette

@@

```{r Linear food-web model, cache=TRUE}
linear_foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

visreg::visreg(linear_foodweb_model, xvar="sc.sqrt.Pref", by="Foodweb", scale="response")
```

@@

<!-- We quantified biased selection on chamber diameter in the following way. First, we focus on multi-chambered galls where there is evidence of both survival and parasitism. The idea is that galls from the same clutch should be similar in size; therefore, any selection on diameter would be apparent. If we assume that this is all due to the effect of parasitism on larval development, truncating gall diameter, then we can consider this new selection differential to be the result of confounding factors. Note that this method likely overestimates the confounding effect of parasitism, since we are assuming that any heterogeneity in chamber diameter (for this subset) is due to parasitism. -->

@@

# Reproduce Figure 2 of main manuscript

@@

# Get legend
#legend_foodwebegglarval_grads <- get_legend(plot_foodwebegglarval_directional_grads)

# Format plots for manuscript
#plot_foodwebegglarval_grads <- plot_grid(
#  plot_foodwebegglarval_directional_grads + theme(legend.position = "none", axis.title = element_blank()),
#  plot_foodwebegglarval_quadratic_grads + theme(legend.position = "none", axis.title = element_blank()),
#  plot_foodwebegglarval_correlational_grads + theme(legend.position = "none", axis.title = element_blank()), 
#  nrow=2, align="hv", labels = "")
#plot_legend_foodwebegglarval_grads <- ggdraw(plot_foodwebegglarval_grads) + draw_grob(legend_foodwebegglarval_grads, x = 0.7, y=-0.2)
#y_title_foodwebegglarval_grads <- ggdraw() + draw_label("Selection gradient (SDs)", angle = 90)

#figure_foodwebegglarval_grads <- plot_grid(y_title_foodwebegglarval_grads, plot_legend_foodwebegglarval_grads, ncol=2, rel_widths = c(0.05,1)) 
#figure_foodwebegglarval_grads

@@

# Plot mean fitness
plot_foodwebegglarval_mean_fitness <- tidy_foodwebegglarval_alphas %>%
  filter(type!="Diff", term=="(Intercept)") %>%
  ggplot(., aes(x=type)) +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
 # geom_text(data=filter(tidy_foodwebegglarval_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.9, x=1.5, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
  scale_x_discrete(name="Parasitoids", breaks=c("Complex","Simple","Larval"), labels=c("Egg + Larval","Egg","Larval")) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels) +
  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels)

# Plot linear trait-fitness relationaships
plot_foodwebegglarval_linear_coefs <- tidy_foodwebegglarval_alphas %>%
  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
  ggplot(., aes(x=term)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  #geom_text(data=filter(tidy_foodwebegglarval_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
  #          aes(y=P_asterisk_foodwebegglarval_coefs, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodwebegglarval_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam]","alpha[Clutch]","alpha[Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels) +
  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels)

# Plot quadratic trait-fitness relationships
plot_foodwebegglarval_quadratic_coefs <- tidy_foodwebegglarval_alphas %>%
  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
  ggplot(., aes(x=term, color=type)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  #geom_text(data=filter(tidy_foodwebegglarval_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
  #          aes(y=P_asterisk_foodwebegglarval_coefs, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodwebegglarval_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Diam]","alpha[Clutch:Clutch]","alpha[Pref:Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels) +
  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels)

# Plot correlational trait-fitness relationaships
plot_foodwebegglarval_correlational_coefs <- tidy_foodwebegglarval_alphas %>%
  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
  ggplot(., aes(x=term, color=type)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
 # geom_text(data=filter(tidy_foodwebegglarval_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
  #          aes(y=P_asterisk_foodwebegglarval_coefs, label=P_cutoff), size=P_size, color="black") +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodwebegglarval_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Clutch]","alpha[Diam:Pref]","alpha[Clutch:Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels) +
  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels)

@@

```{r Egg vs. egg ptoid model, cache=TRUE}
# excludes cases of larval-parasitism from Complex food web
#eggegg_df <- #filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & ectos < 1) %>%
  #mutate(gall_survival = ifelse(gall_survival==1,0,1)) # attempt to look at survival of egg parasitoid

@@

biased_eggegg_model <- update(biased_foodweb_model, data=biased_eggegg_df)

visreg::visreg(eggegg_model, xvar="sc.sqrt.Pref", by="sc.Diam", scale="response", cond = list(Foodweb="Simple"))
visreg::visreg(eggegg_model, xvar="sc.sqrt.Pref", by="sc.Diam", scale="response", cond = list(Foodweb="Complex"))
visreg::visreg(eggegg_model, xvar="sc.Diam", by="sc.sqrt.Pref", scale="response", cond = list(Foodweb="Simple"))
visreg::visreg(eggegg_model, xvar="sc.Diam", by="sc.sqrt.Pref", scale="response", cond = list(Foodweb="Complex"))
```

@@

# To determine whether I should adjust any coefficients associated with chamber diameter, e.g. quadratic and correlation terms, I conducted a quick simulation. In the simulation, I assumed that if the larva survive, then the chamber diameter was the corrent one. However, if the larva did not survive, its size could be due to both its size and parasitism. I assumed a constant value of parasitism effect on gall size.

@@

# Make plots
AF_uni_plots <- plot_grid(AF_uni_Diam + theme(legend.position = "none"), 
                                           #   axis.text.x = element_text(size=10),
                                          #    axis.title.x = element_text(size=11)), 
                       AF_uni_Pref + theme(legend.position = "none", 
                                           axis.title.y = element_blank()) + xlab("Preference (SDs)"),
                                           #axis.text.x = element_text(size=10),
                                           #axis.title.x = element_text(size=11)),
                      AF_uni_Clutch + theme(legend.position = "none",
                                             axis.title.y = element_blank()), 
                                            # axis.text.x = element_text(size=10),
                                            # axis.title.x = element_text(size=11)),
                    # legend_only + theme(legend.position = "none",                          
                    #                         axis.title.y = element_blank(), 
                    #                         axis.text.x = element_text(size=10),
                    #                         axis.title.x = element_text(size=11)),
                       labels = "AUTO", nrow = 1, align='hv')

@@

eggptoid_selection_plot
save_plot(filename = "selection_on_Platygaster.pdf", plot = eggptoid_selection_plot, base_height = 4) # base_height = 6
```

```{r Egg-Parasitoid-Selection-linear, echo=F}
linear_eggptoid_plot_df <- linear_eggegg_RF_Pref$absolute_fitness %>% 
  select(-sc.Diam, -sc.log.Clutch) %>%
  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
  spread(Foodweb, absolute_fitness) %>%
  #filter(ID_group=="average") %>%
  mutate(fitness_difference = Complex-Simple)

@@

RF_Diam_legend_only <- bind_rows(RF_plot_foodweb_Diam_df, RF_plot_egglarval_Diam_df) %>%
  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
  filter(ID_group=="average") %>%
  ggplot(., aes(x=sc.Diam, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Chamber diameter (SDs)") +
  ylab("Relative fitness") +
  scale_color_manual(values = cbPalette[c(6,5,4)], name = "Parasitoids") + # "Food web"
  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
  coord_cartesian(ylim=c(0.2,2)) +
  theme(legend.title.align = 0.5) +
  geom_hline(yintercept=1, linetype="dotted")

# Get legend
RF_uni_legend <- get_legend(RF_legend_only) #  + theme(legend.position = "top")

# Make plots
RF_uni_plots <- plot_grid(RF_Diam_legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
                                             #axis.title.y = element_blank(), 
                                             #axis.text.y = element_blank(),
                                             axis.text.x = element_text(size=10),
                                             axis.title.x = element_text(size=11)),
                     RF_pref_legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
                                             axis.title.y = element_blank(), 
                                             #axis.text.y = element_blank(),
                                             axis.text.x = element_text(size=10),
                                             axis.title.x = element_text(size=11)),
                     RF_legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
                                             axis.title.y = element_blank(), 
                                             #axis.text.y = element_blank(),
                                             axis.text.x = element_text(size=10),
                                             axis.title.x = element_text(size=11)),
                     #  labels = "AUTO", 
                     ncol = 3, align='hv')

@@

# Format plots
AF_landscape_plots <- plot_grid(
  AF_plot_Diam.Clutch + theme(legend.position = "none", 
                              axis.title.x = element_blank(),
                             axis.text.x = element_blank()) +
    #stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") + # mean(RF_Diam.Pref$absolute_fitness$average)
    geom_segment(data = gradients_Diam.Clutch, 
                 aes(x = sc.Diam, y = sc.log.Clutch, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))),
  AF_plot_Clutch.Pref + theme(legend.position = "none", 
                              axis.title.y = element_blank(),
                              axis.text.y = element_blank()) + xlab("Preference (SDs)") +
    #stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
    geom_segment(data = gradients_Clutch.Pref, 
                 aes(x = sc.sqrt.Pref, y = sc.log.Clutch, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))), 
  AF_plot_Diam.Pref + theme(legend.position = "none") + ylab("Preference (SDs)") +
    #stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
    geom_segment(data = gradients_Diam.Pref, 
                 aes(x = sc.Diam, y = sc.sqrt.Pref, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))), 
  nrow=2, align="hv", labels = "AUTO")

>>>>

---
title: "Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*"
author: "Matthew A. Barbour"
date: "`r Sys.Date()`"
output: github_document
# Trying github_document for easy viewing on github
#  prettydoc::html_pretty:
#    theme: architect
#    highlight: github
fontsize: 12pt
---

@@

  # subset data for analysis
  filter(phenology == "early", Location == "tree",
         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
  filter(Treatment.focus == "Ectoparasitoid exclusion" & ectos < 1 | Treatment.focus == "Control") %>% # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
  mutate(Foodweb = ifelse(Treatment.focus=="Control","Complex","Simple"),
         gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
         # transform and scale traits to approximate multivariate normal assumption
         sc.Diam = as.numeric(scale(Gall_Height_mm)), 
         sc.log.Clutch = as.numeric(scale(log(gall_individuals))), 
         sc.sqrt.Pref = as.numeric(scale(sqrt(Density_per_100_shoots))))

@@

## Bootstrap fitness estimates
bootstrap_fitness <- function(logistic_model, newdata, bootstraps, intervals=c(0.025,0.975)){

  # Absolute fitness
  get_absolute_fitness <- function(.) predict(., newdata=newdata, type="response", re.form=~0)

@@

  if(is.null(bootstraps) == FALSE){
    set.seed(34) # make sure results are reproducible
    get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

@@

@@

## Color-blind friendly palette: http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/

@@

```{r Linear food-web model, cache=TRUE}
linear_foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

@@

@@

@@

@@

# Plot mean fitness
plot_foodwebegglarval_mean_fitness <- tidy_foodwebegglarval_alphas %>%
  filter(type!="Diff", term=="(Intercept)") %>%
  ggplot(., aes(x=type)) +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  scale_y_continuous(name="larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
  scale_x_discrete(name="Parasitoids", breaks=c("Complex","Simple","Larval"), labels=c("Egg + Larval","Egg","Larval")) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels) +
  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels)

# Plot linear trait-fitness relationaships
plot_foodwebegglarval_linear_coefs <- tidy_foodwebegglarval_alphas %>%
  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
  ggplot(., aes(x=term)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodwebegglarval_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam]","alpha[Clutch]","alpha[Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels) +
  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels)

# Plot quadratic trait-fitness relationships
plot_foodwebegglarval_quadratic_coefs <- tidy_foodwebegglarval_alphas %>%
  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
  ggplot(., aes(x=term, color=type)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodwebegglarval_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Diam]","alpha[Clutch:Clutch]","alpha[Pref:Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels) +
  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels)

# Plot correlational trait-fitness relationaships
plot_foodwebegglarval_correlational_coefs <- tidy_foodwebegglarval_alphas %>%
  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
  ggplot(., aes(x=term, color=type)) +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
  scale_y_continuous(name="Coefficient", limits=y_limits_foodwebegglarval_coefs) +
  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Clutch]","alpha[Diam:Pref]","alpha[Clutch:Pref]"))) +
  facet_wrap(~coefficient_type) +
  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels) +
  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels)

@@

```{r Egg vs. egg ptoid model, cache=TRUE}

@@

biased_eggegg_model <- update(biased_foodweb_model, data=biased_eggegg_df)
```

@@

# To determine whether I should adjust any coefficients associated with chamber diameter, e.g. quadratic and correlation terms, I conducted a quick simulation. In the simulation, I assumed that if the larva survive, then the chamber diameter was the correct one. However, if the larva did not survive, its size could be due to both its size and parasitism. I assumed a constant value of parasitism effect on gall size.

@@

# Make plots
AF_uni_plots <- plot_grid(AF_uni_Diam + theme(legend.position = "none"), 
                       AF_uni_Pref + theme(legend.position = "none", 
                                           axis.title.y = element_blank()) + xlab("Preference (SDs)"),
                      AF_uni_Clutch + theme(legend.position = "none",
                                             axis.title.y = element_blank()), 
                       labels = "AUTO", nrow = 1, align='hv')

@@

eggptoid_selection_plot
save_plot(filename = "selection_on_Platygaster.pdf", plot = eggptoid_selection_plot, base_height = 4) # base_height = 6 is to large for PDF of manuscript
```

```{r Egg-Parasitoid-Selection-linear, echo=F}
linear_eggptoid_plot_df <- linear_eggegg_RF_Pref$absolute_fitness %>% 
  select(-sc.Diam, -sc.log.Clutch) %>%
  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
  spread(Foodweb, absolute_fitness) %>%
  mutate(fitness_difference = Complex-Simple)

@@

RF_Diam_legend_only <- bind_rows(RF_plot_foodweb_Diam_df, RF_plot_egglarval_Diam_df) %>%
  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
  filter(ID_group=="average") %>%
  ggplot(., aes(x=sc.Diam, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Chamber diameter (SDs)") +
  ylab("Relative fitness") +
  scale_color_manual(values = cbPalette[c(6,5,4)], name = "Parasitoids") + 
  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
  coord_cartesian(ylim=c(0.2,2)) +
  theme(legend.title.align = 0.5) +
  geom_hline(yintercept=1, linetype="dotted")

# Get legend
RF_uni_legend <- get_legend(RF_legend_only)

# Make plots
RF_uni_plots <- plot_grid(RF_Diam_legend_only + theme(legend.position = "none", 
                                             axis.text.x = element_text(size=10),
                                             axis.title.x = element_text(size=11)),
                     RF_pref_legend_only + theme(legend.position = "none",                          
                                             axis.title.y = element_blank(), 
                                             axis.text.x = element_text(size=10),
                                             axis.title.x = element_text(size=11)),
                     RF_legend_only + theme(legend.position = "none",                          
                                             axis.title.y = element_blank(), 
                                             axis.text.x = element_text(size=10),
                                             axis.title.x = element_text(size=11)),
                     ncol = 3, align='hv')

@@

# Format plots
AF_landscape_plots <- plot_grid(
  AF_plot_Diam.Clutch + theme(legend.position = "none", 
                              axis.title.x = element_blank(),
                             axis.text.x = element_blank()) +
    geom_segment(data = gradients_Diam.Clutch, 
                 aes(x = sc.Diam, y = sc.log.Clutch, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))),
  AF_plot_Clutch.Pref + theme(legend.position = "none", 
                              axis.title.y = element_blank(),
                              axis.text.y = element_blank()) + xlab("Preference (SDs)") +
    geom_segment(data = gradients_Clutch.Pref, 
                 aes(x = sc.sqrt.Pref, y = sc.log.Clutch, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))), 
  AF_plot_Diam.Pref + theme(legend.position = "none") + ylab("Preference (SDs)") +
    geom_segment(data = gradients_Diam.Pref, 
                 aes(x = sc.Diam, y = sc.sqrt.Pref, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))), 
  nrow=2, align="hv", labels = "AUTO")
